---
title: "`r paste0('Objects in Memory ', basename(getwd()))`"
output: 
  html_document: 
    self_contained: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages = FALSE, warnings = FALSE)
library(dplyr)
```


```{r RData and their objects}

data_objects <- purrr::map(list.files("images", pattern = "R[dD]ata$", full.names = TRUE) %>% setNames(nm = .), ~{
  e <- new.env()
  load(.x, envir = e)
  .out <- data.frame(objects = ls(envir = e, all.names = T), stringsAsFactors = F) %>% 
  rowwise() %>% 
  mutate(`size(MB)` = as.numeric(stringr::str_extract(format(object.size(get0(objects, envir = e)), units = "MB"), "[\\d\\.]+")))
})
```


```{r 'Which Objects are unused in the app'}
files <- c(server = "server", u = "ui", global = "global")
files <- purrr::map(files, ~{
  lines <- readr::read_lines(fs::path(.x, ext = "R"))
})

objects_used <- purrr::map(data_objects, ~{
  .occurences <- purrr::map(setNames(.x$objects, .x$objects), ~{
    .obj <- .x
    .present <- purrr::map_chr(files, ~{
      .line <- grep(.obj, .x, fixed = TRUE)
      if (vctrs::vec_is_empty(.line)) {
        .out <- paste0("0")
      } else {
        .out <- paste0(.line, collapse = ", ")
      } 
      .out
    })
  })
  dplyr::bind_cols(.x, dplyr::bind_rows(.occurences))
})
objects_tables <- purrr::imap(objects_used, ~{
  .rdata <- .y
  .table <- .x
  dplyr::mutate(.table, keep = dplyr::if_else(u == "0" & server == "0" & global == "0", FALSE, TRUE), .before = "server") %>% 
    dplyr::arrange(desc(`size(MB)`))
})
```


```{r 'Compute total savings'}
.mem_rem <- sum(purrr::map_dbl(objects_tables, ~{sum(.x$`size(MB)`[!.x$keep])}))
.mem_tot <- sum(purrr::map_dbl(objects_tables, ~{sum(.x$`size(MB)`)}))
```


## Total Possible Memory Savings
Current memory usage: `r paste0(.mem_tot, "MB")`

Number of simultaneous users that can currently be supported with 8GB of RAM: `r 8000 %/% .mem_tot`

Amount of memory that can be removed: `r paste0(.mem_rem, "MB | ", round(.mem_rem/.mem_tot*100,3),"%")`

Number of simultaneous users that will be supported with 8GB of RAM: `r 8000 %/% (.mem_tot - .mem_rem)`

To recoup this memory, it is easiest to simply maintain an image at the bottom of `daily_update_00.R` with a list of all the objects necessary for each app to run. 
The image necessary for `r basename(getwd())` to run is:

```{r 'Image call' }
.current_dir <- basename(getwd())
.call <- unique(unlist(purrr::map(objects_tables, ~{.x$objects[.x$keep]}), use.names = FALSE))
.call <- paste0(stringr::str_subset(.call, "^\\.", negate = T), collapse = ", ")
suppressWarnings(.call$file <-  fs::path("..", .current_dir, "data", .current_dir, ext = "RData"))
htmltools::tags$code(paste0("save(", .call[[1]],", compress = FALSE, file = '", .call$file,"')"))
```

See [COHHIO_HMIS#94](https://github.com/COHHIO/COHHIO_HMIS/issues/94) for details and discussion.

# Tables
The tables below provide the following information per RData image:

 - objects: the name of the object in the file
 - size(MB): the size of the object in MB
 - keep: whether the object occurs anywhere in server,global or ui.R
 - server,global,u: the line numbers in the respective file in which the object appears

There is an accompanying call to `rm` that specifies the objects that can be safely removed after each script.

```{r 'Display results'}
do.call(htmltools::tagList, purrr::imap(objects_tables, ~{
  .mem_tot <- sum(.x$`size(MB)`)
  .mem_rem <- sum(.x$`size(MB)`[!.x$keep])
  htmltools::tagList(
    htmltools::tags$h5(.y),
    htmltools::tags$p("Objects that can be removed: "),
    htmltools::tags$p(paste0("rm(list = c(", paste0(paste0("'",.x$objects[!.x$keep],"'"), collapse = ","),"))")),
    htmltools::tags$p(paste0("Total memory savings: ", sum(.x$`size(MB)`[!.x$keep])), "MB | ", round(.mem_rem / .mem_tot * 100, 3),"%"),
    DT::datatable(.x)
  )
}))
```
