---
title: "Eva Metadata Analysis"
author: "Eva Dev Team"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)
library(tidyverse)
library(lubridate)
library(patchwork)
library(gt)

# Ignore this but don't remove it :)---------------------------------------

# this is irrelevant to the metadata analysis but this script needs to be run
# every week or so, so by putting it here, it is updating the EvaChecks.xlsx
# document on GitHub in case there were any edits to checks!

source(here("app_checks.R"))

# Instructions ------------------------------------------------------------

# whenever DDS uploads the metadata zip file to ACE (S:\Projects\CE_Data_Toolkit\Eva metadata), navigate to the metadata-analysis directory in your Eva RStudio project, click Upload, then Choose File (not Browse), then upload that zip file. Click OK or whatever. Run this.

visits <-
  read_lines(here("www/metadata/site_visits.txt"))

uploads <-
  read_lines(here("www/metadata/upload_metadata.txt"))

new_way <-
  read_csv(here(paste0(
    "metadata-analysis/metadata.csv"
  ))) %>%
  group_by(SessionToken) %>%
  mutate(sessionTime = difftime(max(Datestamp), min(Datestamp), units = "mins"),
         is_timeout = sessionTime >= 10 & sessionTime < 11,
         Details = if_else(Details == "Session started" & is_timeout == TRUE , 
                            "Session restarted after timeout", 
                           Details
                           )
         ) %>%
  ungroup() %>%
  select("SessionID" = SessionToken,
         "Date" = Datestamp,
         "Event" = Details) %>%
  mutate(WeekEnding = ceiling_date(Date, unit = "week", week_start = 1))

# building dataset
visits_df <- data.frame(everything = visits) %>%
  mutate(
    SessionID = str_squish(str_sub(everything, 1L, 33L)),
    Date = ymd_hms(str_squish(str_sub(everything, 35L, 54L))),
    WeekEnding = ceiling_date(Date, unit = "week", week_start = 1),
    Event = str_squish(str_sub(everything, 57L, nchar(everything))),
    everything = NULL
  )

uploads_df <- data.frame(everything = uploads) %>%
  mutate(
    SessionID = str_squish(str_sub(everything, 1L, 33L)),
    Date = ymd_hms(str_squish(str_sub(everything, 35L, 54L))),
    WeekEnding = ceiling_date(Date, unit = "week", week_start = 1),
    Event = str_squish(str_sub(everything, 57L, nchar(everything))),
    everything = NULL
  )

old_way <- rbind(uploads_df, visits_df) %>%
  mutate(
    Event = case_when(
      Event == "Unsuccessful - not structurally valid" ~
        "Unsuccessful upload - not structurally valid",
      Event == "Unsuccessful - not hashed" ~
        "Unsuccessful upload - not hashed",
      Event == "Unsuccessful - wrong dataset" ~
        "Unsuccessful upload - wrong/incomplete dataset",
      Event == "Unsuccessful - file was mistructured" ~
        "Unsuccessful upload - file was mistructured",
      TRUE ~ Event
    )
  )

staging <- rbind(new_way, old_way) %>%
  mutate(Event = if_else(Event == "Session started", "Site hits", Event),
         WeekEnding = as.Date(WeekEnding))

all <- staging %>%
  filter(WeekEnding < ceiling_date(max(ymd_hms(staging$Date)),
                                   unit = "week"))

counts <- count(all, WeekEnding, Event) %>%
  arrange(WeekEnding, desc(n))
```

# {.tabset}

## Eva Usage Statistics

Eva logs do not tell us how many Eva users there are, but a count of times someone came to Eva initially or refreshed Eva in their browser. A single user will likely be represented in these counts multiple times. Eva was released on December 19, 2022 and clearly generated a lot of interest up front.

```{r fig.width=8, fig.height=5}

counts %>%
  filter(Event == "Site hits") %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line() +
  geom_point() +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(
    title = "Eva Site Hits",
    x = "Week Ending",
    y = ""
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## Uploads

The first step a user must take to make Eva useful is to upload a hashed HMIS CSV Export, as defined in the [HMIS CSV Format Specifications](https://hudhdx.info/Resources/Vendors/HMIS_CSV_Specifications_FY2022_v1.3.pdf). These exports are created and maintained by HMIS vendors, so any issues found with the structure of the export would be fixed by a community's HMIS vendor. Some issues are non-consequential, and so are categorized as either Warnings or Errors, however some file structure issues would cause Eva to crash or return unexpected results. Eva will reject an export if they have any high priority issue like this.

The reasons Eva will reject an export are if the export:

* is not hashed
* is not zipped or is otherwise not structured properly
* does not contain all the csv files (could be an APR or LSA)
* contains certain vital data elements with misspelled column names
* contains certain vital data elements where the data type is incorrect
* contains a csv file with the wrong number of columns
* has duplicate unique IDs in certain files
* contains certain vital data elements where there are nulls where they are not allowed
* has clients/projects represented in the Enrollment file but not in the Client/Project file 


```{r fig.width=8, fig.height=5}

counts %>%
  filter(str_detect(Event, " upload")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line() +
  geom_point() +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Eva Uploads",
       x = "Week Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))

```

## Downloads

Once an Eva user has uploaded their HMIS CSV Export successfully, they can use Eva to help them manage their HMIS data quality and gain other insights. These downloads consist of summary and detail data, whereas the app user interface mostly displays only summary data.

Eva did not begin tracking downloads until December 29, 2022.

```{r fig.width=8, fig.height=5}

counts %>%
  filter(str_detect(Event, "Download")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line() +
  geom_point() +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Eva Downloads",
       x = "Week Ending",
       y = "",
       caption = "Download data not collected until Dec 29, 2022.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))

```

## Data

Below are the counts by Week. A week here is counted Monday to Sunday.

<br>

```{r data}
gt(counts %>%
     select(
       "Week Ending" = WeekEnding,
       Event,
       "Count" = n
     ))
```

# {-}

