---
title: "Eva Metadata Analysis"
author: "Eva Dev Team"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)
library(tidyverse)
library(lubridate)
library(patchwork)
library(gt)
library(scales)

# Instructions ------------------------------------------------------------

# whenever DDS uploads the metadata zip file to ACE (S:\Projects\CE_Data_Toolkit\Eva metadata), navigate to the metadata-analysis directory in your Eva RStudio project, click Upload, then Choose File (not Browse), then upload that zip file. Click OK or whatever. Run this.

visits <- read_lines(here("metadata-analysis/metadata/site_visits.txt"))

uploads <- read_lines(here("metadata-analysis/metadata/upload_metadata.txt"))


session_data <- read_csv(here("metadata-analysis/metadata/sessiondata.csv")) %>%
  group_by(SessionToken) %>%
  count(CoC)

new_way <-
  read_csv(here("metadata-analysis/metadata/metadata.csv")) %>% # <- don't change this
  # ^ change where your file is in your project directory
  group_by(SessionToken) %>%
  mutate(sessionTime = difftime(max(Datestamp), min(Datestamp), units = "mins"),
         is_timeout = sessionTime >= 10 & sessionTime < 11,
         Details = if_else(Details == "Session started" & is_timeout == TRUE , 
                            "Session restarted after timeout", 
                           Details
                           )
         ) %>%
  ungroup() %>%
  select("SessionID" = SessionToken,
         "Date" = Datestamp,
         "Event" = Details) %>%
  mutate(WeekEnding = ceiling_date(Date, unit = "week", week_start = 1),
         MonthEnding = floor_date(Date, unit = "month"),
         EventCategory = case_when(
           Event %in% c(
             "Unsuccessful upload - not structurally valid",
             "Unsuccessful upload - not hashed",
             "Unsuccessful upload - wrong dataset",
             "Unsuccessful upload - wrong/incomplete dataset",
             "Unsuccessful upload - file was mistructured",
             "Unsuccessful upload - zip file was misstructured",
             "Unsuccessful upload - out of date HMIS CSV Export"
           )
           ~ "Unsuccessful upload",
           Event %in% c("Successful upload") ~ "Successful upload",
           grepl("Downloaded", Event, ignore.case = TRUE) ~ "Downloaded",
           TRUE ~ "Other"
         )) %>%
  filter(today() >= WeekEnding)

# building dataset
visits_df <- data.frame(everything = visits) %>%
  mutate(
    SessionID = str_squish(str_sub(everything, 1L, 33L)),
    Date = ymd_hms(str_squish(str_sub(everything, 35L, 54L))),
    WeekEnding = ceiling_date(Date, unit = "week", week_start = 1),
    MonthEnding = floor_date(Date, unit = "month"),
    Event = str_squish(str_sub(everything, 57L, nchar(everything))),
    everything = NULL
  )

uploads_df <- data.frame(everything = uploads) %>%
  mutate(
    SessionID = str_squish(str_sub(everything, 1L, 33L)),
    Date = ymd_hms(str_squish(str_sub(everything, 35L, 54L))),
    WeekEnding = ceiling_date(Date, unit = "week", week_start = 1),
    MonthEnding = floor_date(Date, unit = "month"),
    Event = str_squish(str_sub(everything, 57L, nchar(everything))),
    everything = NULL
  )

old_way <- rbind(uploads_df, visits_df) %>%
  mutate(
    EventCategory = case_when(
      Event %in% c(
        "Unsuccessful upload - not structurally valid",
        "Unsuccessful upload - not hashed",
        "Unsuccessful upload - wrong dataset",
        "Unsuccessful upload - wrong/incomplete dataset",
        "Unsuccessful upload - file was mistructured",
        "Unsuccessful upload - zip file was misstructured",
        "Unsuccessful upload - out of date HMIS CSV Export")
      ~ "Unsuccessful upload",
      Event %in% c("Successful upload") ~ "Successful Upload",
      grepl("Downloaded", Event, ignore.case = TRUE) ~ "Downloaded",
      TRUE ~ "Other"
    )
  )

staging <- rbind(new_way, old_way) %>%
  mutate(Event = if_else(Event == "Session started", "Site hits", Event),
         WeekEnding = as.Date(WeekEnding),
         MonthEnding = as.Date(MonthEnding))

#all_week <- staging %>%
#  filter(WeekEnding >= ceiling_date(max(ymd_hms(staging$Date)),
#                                   unit = "week")- weeks(8))

all_week <- staging %>%
  filter(WeekEnding >= ceiling_date(max(as_datetime(as.POSIXct(staging$Date))),
                                   unit = "week")- weeks(8))

all_month <- staging %>%
  filter(MonthEnding >= ceiling_date(max(as_datetime(as.POSIXct(staging$Date))),
                                   unit = "month")- months(12))

all_month_history <- staging %>%
  filter(MonthEnding < ceiling_date(max(as_datetime(as.POSIXct(staging$Date))),
                                   unit = "month"))

counts_by_week <- count(all_week, WeekEnding, Event) %>%
  arrange(WeekEnding, desc(n))

counts_by_month <- count(all_month, MonthEnding, Event) %>%
  arrange(MonthEnding, desc(n))

counts_by_month_history <- count(all_month_history, MonthEnding, Event) %>%
  arrange(MonthEnding, desc(n))

counts_category_week <- count(all_week, WeekEnding, EventCategory) %>%
  arrange(WeekEnding, desc(n))

counts_category_month <- count(all_month, MonthEnding, EventCategory) %>%
  arrange(MonthEnding, desc(n))

end_date_last6months <- floor_date(Sys.Date(), "month") - days(1)

start_date_last6months <- end_date_last6months %m-% months(6) + days(1)

staging_last6months <- staging %>%
  filter(Date >= start_date_last6months & Date <= end_date_last6months)

eva_colors <- c("#16697a", "#C2462E", "#71B4CB", "#73655E",
                 "#C1DDD7","#FCB248","#CEEfb7", "#71B58B")

```


# {.tabset}

## Eva Usage Statistics

Eva logs do not tell us how many Eva users there are, but a count of times someone came to Eva initially or refreshed Eva in their browser. A single user will likely be represented in these counts multiple times. Eva was released on December 19, 2022 and clearly generated a lot of interest up front.

Adjusted site hits give a count of unique sessions where a tab other than "Home" was clicked on at least once. Raw site hits are not shown here because security scans have artificially increased the total count of raw site hits. Identifying sessions where a tab other than "Home" has been selected provides a better picture of real engagement with Eva.

```{r fig.width=10, fig.height=5}

all_week_deduped <- all_week %>% 
  filter(str_detect(Event, "User on tab")) %>% 
  filter(!(Event %in% c('User on tabHome'))) %>%
  distinct(SessionID, .keep_all = TRUE)

counts_by_week_hits <- count(all_week_deduped, WeekEnding, Event) %>%
  group_by(WeekEnding) %>%
  summarise(Hits = sum(n)) %>% 
  arrange(WeekEnding, desc(Hits))

counts_by_week_hits %>%
  ggplot(aes(x = WeekEnding, y = Hits, label = Hits)) +
  geom_line() +
  geom_point() +
  geom_text(nudge_x = 1.25, color = "gray15", check_overlap = TRUE) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m/%d") +
  labs(
    title = "Weekly Eva Adjusted Site Hits",
    x = "Week Ending",
    y = ""
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  ylim(0, NA)
  
```

```{r fig.width=10, fig.height=5}

all_month_deduped <- all_month %>% 
  filter(str_detect(Event, "User on tab")) %>% 
  filter(!(Event %in% c('User on tabHome'))) %>%
  distinct(SessionID, .keep_all = TRUE)

counts_by_month_hits <- count(all_month_deduped, MonthEnding, Event) %>%
  group_by(MonthEnding) %>%
  summarise(Hits = sum(n)) %>% 
  arrange(MonthEnding, desc(Hits))

counts_by_month_hits %>%
  ggplot(aes(x = MonthEnding, y = Hits, label = Hits)) +
  geom_line() +
  geom_point() +
  geom_text(nudge_x = 9, color = "gray15", check_overlap = TRUE) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%B") +
  labs(
    title = "Monthly Eva Adjusted Site Hits",
    x = "Month Ending",
    y = ""
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
  
```

## Tabs Visited

```{r fig.width=8.75, fig.height=6}

staging_last6months %>%
  filter(str_detect(Event, "User on") & 
           !(Event %in% c("User on tabHome", "User on tabUpload", "User on"))
         & !str_detect(Event, "DEMO MODE")) %>%
  distinct(SessionID, Event, .keep_all = TRUE) %>%
  mutate(Tab = case_when(
    str_detect(Event, "tabChangelog") ~ "Changelog",
    str_detect(Event, "tabClientCount") ~ "Client Counts",
    str_detect(Event, "tabDQOrg") ~ "Organization DQ",
    str_detect(Event, "tabDQSystem") ~ "System DQ",
    str_detect(Event, "tabLocalSettings") ~ "Local Settings",
    str_detect(Event, "tabPDDE") ~ "PDDE DQ",
    str_detect(Event, "tabSystemOverview") ~ "System Overview",
    str_detect(Event, "tabGlossary") ~ "Glossary",
    TRUE ~ as.character(Event)), 
    Tab = factor(Tab, levels = c("Local Settings", "Client Counts", "PDDE DQ", "System DQ", "Organization DQ", "System Overview", "Glossary", "Changelog"))) %>%
  count(Tab) %>%
  ggplot(aes(x = Tab, y = n, fill = Tab)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(n/sum(n))), color = "gray15", vjust = -0.5) +
  scale_fill_manual(values = 
                   c("Changelog" = "#16697a",
                      "Client Counts" = "#C2462E",
                      "Organization DQ" = "#71B4CB",
                      "System DQ" = "#73655E",
                      "Local Settings" = "#C1DDD7",
                      "PDDE DQ" = "#FCB378",
                      "System Overview" = "#FCB248",
                      "Glossary" = "#71B58B"
                     )) +
 labs(title = "Tabs Visited in the Last 6 Months",
       x = "Tab",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") +
  guides(fill = guide_legend(ncol = 2))

```

```{r fig.width=7, fig.height=6}
# 
# staging %>%
#   filter(str_detect(Event, "User on") & 
#            Date >= as.Date("2023-01-01") & Date <=("2023-06-30") &
#            !(Event %in% c("User on tabHome", "User on tabUpload", "User on"))) %>%
#   distinct(SessionID, Event, .keep_all = TRUE) %>%
#   mutate(Tab = case_when(
#     str_detect(Event, "tabChangelog") ~ "Changelog",
#     str_detect(Event, "tabClientCount") ~ "Client Counts",
#     str_detect(Event, "tabDQOrg") ~ "Organization DQ",
#     str_detect(Event, "tabDQSystem") ~ "System DQ",
#     str_detect(Event, "tabLocalSettings") ~ "Local Settings",
#     str_detect(Event, "tabPDDE") ~ "PDDE DQ",
#     TRUE ~ as.character(Event)), 
#     Tab = factor(Tab, levels = c("Local Settings", "Client Counts", "PDDE DQ", "System DQ", "Organization DQ", "Changelog"))) %>%
#   count(Tab) %>%
#   ggplot(aes(x = Tab, y = n, fill = Tab)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = scales::percent(n/sum(n))), color = "gray15", vjust = -0.5) +
#   scale_fill_manual(values = 
#                    c("Changelog" = "#f94144",
#                       "Client Counts" = "#f3722c",
#                       "Organization DQ" = "#f8961e",
#                       "System DQ" = "#f9c74f",
#                       "Local Settings" = "#90be6d",
#                       "PDDE DQ" = "#43aa8b")) +
#  labs(title = "Tabs Visited from January 2023 to June 2023",
#        x = "Tab",
#        y = "Count") +
#   theme_minimal() +
#   theme(legend.position = "none") +
#   guides(fill = guide_legend(ncol = 2))

```

## Uploads

The first step a user must take to make Eva useful is to upload a hashed HMIS CSV Export, as defined in the [HMIS CSV Format Specifications](https://hudhdx.info/Resources/Vendors/HMIS_CSV_Specifications_FY2022_v1.3.pdf). These exports are created and maintained by HMIS vendors, so any issues found with the structure of the export would be fixed by a community's HMIS vendor. Some issues are non-consequential, and so are categorized as either Warnings or Errors, however some file structure issues would cause Eva to crash or return unexpected results. Eva will reject an export if they have any high priority issue like this.

The reasons Eva will reject an export are if the export:

* is not hashed
* is not zipped or is otherwise not structured properly
* does not contain all the csv files (could be an APR or LSA)
* contains certain vital data elements with misspelled column names
* contains certain vital data elements where the data type is incorrect
* contains a csv file with the wrong number of columns
* has duplicate unique IDs in certain files
* contains certain vital data elements where there are nulls where they are not allowed
* has clients/projects represented in the Enrollment file but not in the Client/Project file 


```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, " upload")) %>%
  filter(!str_detect(Event, "Successful upload")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(na.rm = FALSE, size=0.8) +
  geom_point(na.rm = FALSE, size=1) +
  geom_text(nudge_x = 0.75, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m/%d") +
  labs(title = "Weekly Eva Unsuccessful Uploads",
       x = "Week Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```

```{r fig.width=10, fig.height=5}

counts_category_week %>%
  filter(str_detect(EventCategory, " upload")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = EventCategory, color = EventCategory, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_brewer(palette = "Set1") +
  scale_x_date(date_breaks = "1 week", date_labels = "%m/%d") +
  labs(title = "Weekly Eva Uploads - Successful vs. Unsuccessful",
       x = "Week Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```


```{r fig.width=10, fig.height=5}

counts_by_month %>%
  filter(str_detect(Event, " upload")) %>%
  filter(!str_detect(Event, "Successful upload")) %>%
  ggplot(aes(x = MonthEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(title = "Monthly Eva Unsuccessful Uploads",
       x = "Month Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```


```{r fig.width=10, fig.height=5}

counts_category_month %>%
  filter(str_detect(EventCategory, " upload")) %>%
  ggplot(aes(x = MonthEnding, y = n, group = EventCategory, color = EventCategory, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = 1, color = "gray15", check_overlap = TRUE) +
  scale_color_brewer(palette = "Set1") +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(title = "Monthly Eva Uploads - Successful vs. Unsuccessful",
       x = "Month Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```

## Downloads

Once an Eva user has uploaded their HMIS CSV Export successfully, they can use Eva to help them manage their HMIS data quality and gain other insights. These downloads consist of summary and detail data, whereas the app user interface mostly displays only summary data.

Eva did not begin tracking downloads until December 29, 2022.

```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Weekly Eva Downloads - Data Quality",
       x = "Week Ending",
       y = "",
       caption = "Download data not collected until Dec 29, 2022.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```


```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(str_detect(Event, "System Overview")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Weekly Eva Downloads - System Overview",
       x = "Week Ending",
       y = "",
       caption = "System Overview downloads not available until October, 2024.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```

```{r fig.width=10, fig.height=5}

counts_by_week_download_types <- counts_by_week %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  mutate(Event2 = case_when((!str_detect(Event, "System Overview")) ~ "DQ download",
                              (str_detect(Event, "Powerpoint"))  ~ "System Overview image/ppt download",
                              (str_detect(Event, "Tabular Data")) ~ "System Overview tabular data download")) %>% 
  group_by(WeekEnding, Event2) %>%
  summarise(n2 = sum(n)) %>%
  arrange(WeekEnding, desc(n2))
  
  
counts_by_week_download_types %>% 
  ggplot(aes(x = WeekEnding, y = n2, group = Event2, color = Event2, label = n2)) +
  geom_line(size=0.75) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Weekly Eva Downloads - DQ and System Overview",
       x = "Week Ending",
       y = "",
       caption = "System Overview downloads not available until October, 2024.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```


```{r fig.width=10, fig.height=5}

counts_category_week %>%
  filter(str_detect(EventCategory, "Download")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = EventCategory, color = EventCategory, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .75, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m/%d") +
  labs(title = "Weekly Eva Downloads - Total Downloads",
       x = "Week Ending",
       y = "",
       caption = "Download data not collected until Dec 29, 2022.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```


```{r fig.width=10, fig.height=5}

counts_by_month %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  #filter(MonthEnding >= as.Date("2023-06-01") & as.Date(MonthEnding) <=("2023-11-30")) %>%
  ggplot(aes(x = MonthEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(title = "Monthly Eva Downloads - Data Quality",
       x = "Month Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```
```{r fig.width=10, fig.height=5}

counts_by_month %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  #filter(MonthEnding >= as.Date("2023-06-01") & as.Date(MonthEnding) <=("2023-11-30")) %>%
  ggplot(aes(x = MonthEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(title = "Monthly Eva Downloads - System Overview",
       x = "Month Ending",
       y = "",
       caption = "System Overview download data not collected until Dec 29, 2022.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```


```{r fig.width=10, fig.height=5}

counts_category_month %>%
  filter(str_detect(EventCategory, "Download")) %>%
  #filter(MonthEnding >= as.Date("2023-06-01") & as.Date(MonthEnding) <=("2023-11-30")) %>%
  ggplot(aes(x = MonthEnding, y = n, group = EventCategory, color = EventCategory, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 month", date_labels = "%B") +
  labs(title = "Monthly Eva Downloads - Total Downloads",
       x = "Month Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```


```{r fig.width=7, fig.height=4}

staging_last6months_downloads <- staging_last6months %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  group_by(Event) %>% 
  count(Event)
  
staging_last6months %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>% 
  group_by(Event, EventCategory) %>% 
  count(Event) %>%
  ggplot(aes(fill=Event, y=n, x=EventCategory)) + 
  geom_bar(position="fill", stat="identity") +
  #scale_color_brewer(palette = "Dark2") +
  scale_fill_manual(values = eva_colors) +
  labs(title = "Proportion of Downloads in Last 6 Months - Data Quality",
       x = "",
       y = "") +
  theme_minimal()

```

```{r fig.width=7, fig.height=4}
           
staging_last6months %>%
  filter(str_detect(Event, "Download")) %>%
  filter(!str_detect(Event, "DEMO MODE")) %>%
  filter(str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>% 
  group_by(Event, EventCategory) %>% 
  count(Event) %>% 
  mutate(EventType = case_when(
    str_detect(Event, "Powerpoint") ~ "Image",
    str_detect(Event, "Tabular") ~ "Tabular"
    )) %>% 
  mutate(`System Overview Description` = case_when(
    str_detect(Event, "Client System Status") ~ "Client System Status",
    str_detect(Event, "System Demographics") ~ "System Demographics",
    str_detect(Event, "System Flow") ~ "System Flow"
    )) %>% 
  ggplot(aes(fill=`System Overview Description`, y=n, x=EventType)) + 
  geom_bar(position="fill", stat="identity") +
  scale_fill_manual(values = eva_colors) +
  labs(title = "Proportion of Downloads in Last 6 Months - System Overview",
       x = "",
       y = "") +
  theme_minimal()

```


## Demo Mode Stats

```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, "Switched to demo mode")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(na.rm = FALSE, size=0.8) +
  geom_point(na.rm = FALSE, size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m/%d") +
  labs(title = "Weekly Switches to Demo Mode",
       x = "Week Ending",
       y = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
  
```

```{r fig.width=8.75, fig.height=6}

staging_last6months %>%
  filter(str_detect(Event, "User on") &
        str_detect(Event, "DEMO MODE") &
           !(Event %in% c("User on tabHome", "User on tabHome - DEMO MODE", "User on tabUpload - DEMO MODE", "User on tabUpload", "User on"))) %>%
  distinct(SessionID, Event, .keep_all = TRUE) %>%
  mutate(Tab = case_when(
    str_detect(Event, "tabChangelog") ~ "Changelog",
    str_detect(Event, "tabClientCount") ~ "Client Counts",
    str_detect(Event, "tabDQOrg") ~ "Organization DQ",
    str_detect(Event, "tabDQSystem") ~ "System DQ",
    str_detect(Event, "tabLocalSettings") ~ "Local Settings",
    str_detect(Event, "tabPDDE") ~ "PDDE DQ",
    str_detect(Event, "tabSystemOverview") ~ "System Overview",
    str_detect(Event, "tabGlossary") ~ "Glossary",
    TRUE ~ as.character(Event)), 
    Tab = factor(Tab, levels = c("Local Settings", "Client Counts", "PDDE DQ", "System DQ", "Organization DQ", "System Overview", "Glossary", "Changelog"))) %>%
  count(Tab) %>%
  ggplot(aes(x = Tab, y = n, fill = Tab)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(n/sum(n))), color = "gray15", vjust = -0.5) +
  scale_fill_manual(values = 
                   c("Changelog" = "#16697a",
                      "Client Counts" = "#C2462E",
                      "Organization DQ" = "#71B4CB",
                      "System DQ" = "#73655E",
                      "Local Settings" = "#C1DDD7",
                      "PDDE DQ" = "#FCB378",
                      "System Overview" = "#FCB248",
                      "Glossary" = "#71B58B"
                     )) +
 labs(title = "Tabs Visited in the Last 6 Months",
       x = "Tab",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none") +
  guides(fill = guide_legend(ncol = 2))

```

```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, "Download")) %>%
  filter(str_detect(Event, "DEMO MODE")) %>%
  filter(!str_detect(Event, "System Overview")) %>%
  filter(!str_detect(Event, "Sys Inflow Outflow")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Weekly Eva Downloads While in Demo Mode - Data Quality",
       x = "Week Ending",
       y = "",
       caption = "") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```


```{r fig.width=10, fig.height=5}

counts_by_week %>%
  filter(str_detect(Event, "Download")) %>%
  filter(str_detect(Event, "DEMO MODE")) %>%
  filter(str_detect(Event, "System Overview")) %>%
  ggplot(aes(x = WeekEnding, y = n, group = Event, color = Event, label = n)) +
  geom_line(size=0.8) +
  geom_point(size=1) +
  geom_text(nudge_x = .5, color = "gray15", check_overlap = TRUE) +
  scale_color_manual(values = eva_colors) +
  scale_x_date(date_breaks = "1 week", date_labels = "%m-%d") +
  labs(title = "Weekly Eva Downloads While in Demo Mode - System Overview",
       x = "Week Ending",
       y = "",
       caption = "System Overview data not available until October 2024.") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))


```

## Data by week

Below are the counts by Week. A week here is counted Monday to Sunday.

<br>

```{r data by week}
gt(counts_by_week %>%
     select(
       "Week Ending" = WeekEnding,
       Event,
       "Count" = n
     ))
```

## Data by month

Below are the counts by Month. 

<br>

```{r data by month}
gt(counts_by_month_history %>%
     select(
       "Month Ending" = MonthEnding,
       Event,
       "Count" = n
     ))
```

# {-}


